%-------------------------
% Resume in Latex
% Original Author : Sourabh Bajaj
% Edited By : Christian Carrico
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{makecell}



\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.875in}  %right margin
\addtolength{\evensidemargin}{-0.875in} %left margin
\addtolength{\textwidth}{1.775in}
\addtolength{\topmargin}{-0.875in}
\addtolength{\textheight}{1.775in}

%section spacing {}{Above}{Below}
\titlespacing{\section}{2pt}{3mm}{3mm}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{#1}
}

\newcommand{\resumeItemListStart}{\begin{itemize}[itemsep=1mm, parsep=0mm, topsep=0mm]}
\newcommand{\resumeItemListEnd}{\end{itemize}}

\newcommand{\sectionHeader}[2]{
	\vspace{5pt}\small{ \textbf{#1} | #2}
}

\newcommand{\projectItem}[2]{
  \vspace{5pt}\small{\textbf{#1}{: #2}} \\
}

\newcommand{\sectionSubHeader}[2]{
	\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
		\quad\textit{\small{#1}} & \textit{\small{#2}}
	\end{tabular*}
}

\newcommand{\Rplus}{\protect\hspace{-.1em}\protect\raisebox{.35ex}{\smaller{\smaller\textbf{+}}}}
\newcommand{\Cpp}{\mbox{C\Rplus\Rplus}\xspace}

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\Huge Christian Carrico}} &  \\
		\footnotesize{github.com/chrismcarrico} &  \footnotesize{chrismcarrico@gmail.com} \\
		\footnotesize{linkedin.com/in/chrismcarricoo} &  \footnotesize{(303) 517-2910} \\
\end{tabular*}

%-----------EDUCATION-----------------
\section{Education}
    \sectionHeader{Colorado State University}{Fort Collins, CO}
    	\sectionSubHeader{Bachelor of Science, Computer Engineering}{Aug. 2012 - Dec. 2017}
    	\sectionSubHeader{Bachelor of Science, Mathematics with a concentration in Information Theory}{Aug. 2015 - Dec. 2017}

%--------PROGRAMMING SKILLS------------
\section{Technical Skills}{
	\begin{small}
	\setlength{\tabcolsep}{1em}
		\begin{tabular*}{\textwidth}{l l l l l l}
			\textbf{Programming:} 		& Python 	& C			& JavaScript 	& SQL 				& LaTeX					\\
							   			& Java 		& \Rplus		& C\# 			&  					& Julia					\\
																															\\
			\textbf{Development Tools:} & Agile 	& OpenMP 	& ASP.NET		& NumPy \& SciPy	& Jupyter Notebooks		\\
										& Git 		& MPI 		& JQuerey 		& Pandas			&						\\
		\end{tabular*}
	\end{small}							
}
%-----------EXPERIENCE-----------------
\section{Experience}
    \sectionHeader{AMRDEC: Athena Lab}{Colorado Springs, CO}
   		\sectionSubHeader{Computer Engineer}{Apr. 2018 - Present}
			\resumeItemListStart
				\resumeItem{Maintained an active Secret Security Clearance: 2014 - present}
		   		\resumeItem{Managed development efforts as the government lead on lab projects by coordinating contractor and government activities }
		   		\resumeItem{Improved lab project development by capturing customer requirements into JIRA to organize sprints for new project features}
		   		\resumeItem{Evaluated small business purposals for technical merit on behalf of the MDA to improve the Modeling and Simulation Big Data effort}
		   		\resumeItem{Engaged with Small Businesses to monitor contract progression, answer technical questions, and steer the contract in a direction that benefits the MDA}
		   		\resumeItem{}
		   \resumeItemListEnd
   	\sectionHeader{CSU Accelerator Research Lab}{Fort Collins, CO}
   		\sectionSubHeader{Engineering Intern}{Aug. 2012 - Aug. 2014}
   			\resumeItemListStart
   				\resumeItem{Modeled custom components in SolidWorks to be used in conjunction with the LINAC magnets and RF cavities}
   				\resumeItem{Worked closely with graduate students and professors to document and test capabilities of lab equipment}
   			\resumeItemListEnd
   	\sectionHeader{Electrical \& Computer Engineering College}{Fort Collins, CO}
   		\sectionSubHeader{Student Ambassador}{Aug. 2012 - Aug. 2014}
   			\resumeItemListStart
   				\resumeItem{Lead ECE departmment activities as an example of the department’s students to educate and encourage potential freshman}
   			\resumeItemListEnd
%-----------PROJECTS-----------------
\section{Projects}
	\projectItem{Classified Data ETL Tool}{Python application to extract data from unstructured and structured sources. }
	\projectItem{Modeling \& Simulation Data Warehouse Architecture Design}{Systematic trade study on different big data tools and solutions to design a warhouse for data produced by simulations}
	\projectItem{COCOM Workflow Assistance Tool}{Web application used by Warfighters to organize the COCOM's tasking, scheduling, and inventory. }
	\projectItem{Snowflake Classification Project}{Python neural network implementation used to classify a large database of snowflakes. }
	\projectItem{C++ Number Factorization Project}{A C++ personal project used to explore and implement the Qaudratic Sieve, a complicated algorithm for factoring large pseudoprimes}
\end{document}
